The Astropy Project

### 2017-12-04 main.tex
Update main.tex
If I'm reading it right, BlackBody1D fits flux densities, not fluxes - correct?

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
commits per contributor as of November 2017.
The relative flatness of this distribution (as demonstrated by its log-log slope of
$-0.5$) shows that the \astropypkg core package has been developed by a broad
contributor base.  A leading group of 6 developers have each added over 1000
commits to the repository, and $\sim 20$ more core contributors with at least
100 commits.
However, the distribution of contribution level (number of commits) continues
from 100 down to a single commit.
In this sense, the development of the core package has been a true community
effort and is not dominated by a single individual.
It is also important to note that the number of commits is only a rough metric
of contribution, as a single commit could be a critical fix in the package or a
fix for a typographical error.
\figurename~\ref{fig:ncommits}, right, shows the number of contributors as a
function of time since the genesis of the \astropypkg core package.
The package is still healthy: new commits are and have been contributed at a
steady rate throughout its existence.

@@

The \package{astropy.modeling} subpackage now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values. In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units. Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed fluxes in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).

>>>>

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
\figurename~\ref{fig:ncommits}, left, shows the distribution of total number of
commits per contributor as of November 2017.
The relative flatness of this distribution (as demonstrated by its log-log slope of
$-0.5$) shows that the \astropypkg core package has been developed by a broad
contributor base.  A leading group of 6 developers have each added over 1000
commits to the repository, and $\sim 20$ more core contributors with at least
100 commits.
However, the distribution of contribution level (number of commits) continues
from 100 down to a single commit.
In this sense, the development of the core package has been a true community
effort and is not dominated by a single individual.
It is also important to note that the number of commits is only a rough metric
of contribution, as a single commit could be a critical fix in the package or a
fix for a typographical error.
\figurename~\ref{fig:ncommits}, right, shows the number of commits as a
function of time since the genesis of the \astropypkg core package.
The package is still healthy: new commits are and have been contributed at a
steady rate throughout its existence.

@@

The \package{astropy.modeling} subpackage now supports the representation, evaluation, and fitting of models using \texttt{Quantity} objects, which attach units to scalar values or arrays of values. In practice, this means that one can, for example, fit a model to data with units and get parameters that also have units out, or initialize a model with parameters with units and evaluate it using input values with different but equivalent units. Using this, we have implemented a blackbody model (\texttt{BlackBody1D}) that can be used to fit observed flux densities in a variety of units and as a function of different units of spectral coordinates (e.g., wavelength or frequency).
